Why Real-World Subgraph Isomorphism is Easy, \\ and What This Means for Graph Databases

### 2016-11-07 paper/paper.tex
Combine EPSRC lines

@@

\author{\name Ciaran McCreesh \thanks{This work was supported by the Engineering and Physical Sciences
           Research Council [grant number EP/K503058/1]} \email c.mccreesh.1@research.gla.ac.uk \\
       \name Patrick Prosser \email patrick.prosser@glasgow.ac.uk \\
       \name James Trimble \thanks{This work was supported by the Engineering and Physical Sciences
           Research Council [grant number EP/M508056/1]} \email j.trimble.1@research.gla.ac.uk \\
   \addr University of Glasgow, Glasgow, Scotland}
\maketitle

>>>>

\newcommand*\samethanks[1][\value{footnote}]{\footnotemark[#1]}

@@

\author{\name Ciaran McCreesh \thanks{This work was supported by the Engineering and Physical Sciences
           Research Council [grant numbers EP/K503058/1 and EP/M508056/1]} \email c.mccreesh.1@research.gla.ac.uk \\
       \name Patrick Prosser \email patrick.prosser@glasgow.ac.uk \\
       \name James Trimble \samethanks \email j.trimble.1@research.gla.ac.uk \\
   \addr University of Glasgow, Glasgow, Scotland}
\maketitle
